Fast and optimal centroiding of faint stars

### 2014-12-12 ms/figure.tex
Update figure.tex

In order to test the accuracy of the method mentioned so far, and to ompare them against each other,
and we need to simulate a large set of stars for which we know the exact position of centroids.
Furthermore, we uniformly draw the centroids within sub-pixel regions. 
We use the Moffat profile \citep{moffat} for our PSF simulations. 
Moffat profile is an analytic model for stellar PSFs. It has broader wings than
a simple Gaussian model. The surface brightness of the Moffat profile is given by
\beq
I(r) = \frac{F(\beta -1)}{\pi \alpha^{2}}[1+(r/\alpha)^{2}]^{-\beta},
\label{mof}
\eeq
where $F$ is the total flux, $\beta$ is a dimensionless paramter, and $\alpha$ is
the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$)
being $2\alpha\sqrt{2^{1/\beta}-1}$. 
We want to investigate the performance of centroiding methods introduced
in section \ref{sec:model} for different background noise levels, and also different
values of $\gamma$. For further simplicity, we set the flux of all stars in our
simulations to unity. Per pixel uncertainties are assumed to be uncorrelated Gaussian,
and we only study the sky-dominated regime.

@@

\beq
  \mathcal{F}_{ij} = \sum_{\mathbf{p}}\frac{1}{\sigma_{p}^{2}}
                \frac{\partial f_{\mathbf{p}}}{\partial \theta_{i}}\frac{\partial f_{\mathbf{p}}}{\partial \theta_{j}},
\ref{fish}
\eeq
where the summation is over pixels, $f_{\mathbf{p}}$ is the value of the Moffat profile at pixel $\mathbf{p}$,
$\theta=\{x_{c},y_{c}\}$, $\sigma_{p}^{2}$ is variance
of the uncorrelated Gaussian noise
\begin{eqnarray}
\langle n(\mathbf{x_{p}}) \rangle &=& 0, \\
\langle n(\mathbf{x_{p}})n(\mathbf{x_{p^{\prime}}}) \rangle &=& \sigma^{2}\delta_{\mathbf{p}\mathbf{p}^{\prime}}. 
\end{eqnarray}

@@

Equation (\ref{crlbmoffat}) implies that at given SNR and $\gamma$
CRLB for each component of centroid is given by $.6846\gamma/\text{SNR}$,
and that a good centroiding technique delivers centroids with
root-mean-squared-error (hereafter RMSE) of each component close to
this number.

@@

In order to test the accuracy of each model, we need to compare
the mean squared error to the Cramer-Rao lower bound (hereafter CRLB).
That is, after finding the centroid error for each model, we
compute the mean in bins of $S/N$ (bins of $\gamma$ in the second experiment).

In practice however, instead of mean squared error, we work with the median squared error.
The reason is that, at the faint end of our simulations (SNR $\leq$ 10),
the unmodified polynomial method leads to some catastrophic failures which
could skew the mean squared centroid error of the sample.
Thus, we use median squared error as a less biased representative
of the performance of different centroiding techniques.

@@

Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}]. As we expected, for all methods, median squared error becomes larger for fainter stars, and for stars with larger $\gamma$. As it can be seen in figure [\ref{1}], centroid estimate obtained from the polynomial method does not saturate the CRLB unless at smaller values of SNR.

>>>>

In order to test the accuracy of the method mentioned so far, and to ompare them against each other,
and we need to simulate a large set of stars for which we know the exact position of centroids.
Furthermore, we uniformly draw the centroids within sub-pixel regions. 
We use the Moffat profile \citep{moffat} for our PSF simulations. 
Moffat profile is an analytic model for stellar PSFs. It has broader wings than
a simple Gaussian model. The surface brightness of the Moffat profile is given by
\beq
I(r) = \frac{F(\beta -1)}{\pi \alpha^{2}}[1+(r/\alpha)^{2}]^{-\beta},
\label{mof}
\eeq
where $F$ is the total flux, $\beta$ is a dimensionless paramter, and $\alpha$ is
the length scale of the Moffat profile, with FWHM (hereafter denoted by $\gamma$)
being $2\alpha\sqrt{2^{1/\beta}-1}$. 
We want to investigate the performance of centroiding methods introduced
in section \ref{sec:method} for different background noise levels, and also different
values of $\gamma$. For further simplicity, we set the flux of all stars in our
simulations to unity. Per pixel uncertainties are assumed to be uncorrelated Gaussian,
and we only study the sky-dominated regime.

@@

\beq
  \mathcal{F}_{ij} = \sum_{\mathbf{p}}\frac{1}{\sigma_{\mathbf{p}}^{2}}
                \frac{\partial f_{\mathbf{p}}}{\partial \theta_{i}}\frac{\partial f_{\mathbf{p}}}{\partial \theta_{j}},
\label{fish}
\eeq
where the summation is over pixels, $f_{\mathbf{p}}$ is the value of the Moffat profile at pixel $\mathbf{p}$,
$\theta=\{x_{c},y_{c}\}$, $\sigma_{\mathbf{p}}^{2}$ is variance
of the uncorrelated Gaussian noise map $n(\mathbf{x_{p}})$
\begin{eqnarray}
\langle n(\mathbf{x_{p}}) \rangle &=& 0, \\
\langle n(\mathbf{x_{p}})n(\mathbf{x_{p^{\prime}}}) \rangle &=& \sigma^{2}\delta_{\mathbf{p}\mathbf{p}^{\prime}}. 
\end{eqnarray}

@@

Equation (\ref{crlbmoffat}) implies that at given SNR and $\gamma$
CRLB for each component of centroid is given by $0.6846\gamma/\text{SNR}$,
and that a good centroiding technique delivers centroids with
root-mean-squared-error (hereafter RMSE) of each component close to
this number.

@@

@@

After finding the centroiding error for each method, we
compute the RMSE in bins of SNR.
Results of the first experiment are shown in Figures [\ref{1}], [\ref{2}], [\ref{3}], [\ref{4}].
As we expected, for all methods, median squared error becomes larger for fainter stars,
and for stars with larger $\gamma$. As it can be seen in figure [\ref{1}],
centroid estimate obtained from the polynomial method does not saturate
the CRLB unless at smaller values of SNR.
